---
title: 'Lab 4: Dynamic Regression'
author: "Taoufik En-Najjary"
date: "14 décembre 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

We will use the time series __austa__ from package __fpp__. It represent the total number of international visitors to Australia each year from 1980 to 2010. We will fit both a deterministic and a stochastic trend model to these data.

1. Plot the time series?
2. Fit an ARIMA model for this serie and plot a forecast
```{r, eval=FALSE}
library(ggplot2)
library(forecast)
plot.ts(austa)
fit <- auto.arima(austa)
ggtsdisplay(residuals(fit))
Box.test(residuals(fit), type="Ljung")
plot(forecast(fit))

```


Now, we consider the following model

$y_t = \alpha + \beta t + n_t$
whare $n_t$ is an arima process

3. fit the proposed model (use of __Arima()__ function)
4. compare the forecast obtained with both models
```{r, eval=FALSE}
fit2 <- auto.arima(austa,d=0,xreg=1:length(austa))
ggtsdisplay(residuals(fit2))
Box.test(residuals(fit2), type="Ljung")
plot(forecast(fit2,   xreg = length(austa) + 1:10))
```

